---
title: "Physical Pragmatics (Experiment 4)"
output:
  pdf_document: default
  html_document:
    code_folding: hide
    df_print: paged
---

```{r setup, echo=FALSE}
# Set the working directory.
knitr::opts_knit$set(root.dir=normalizePath(".."))

# Turn off compile messages and warnings.
knitr::opts_chunk$set(message=FALSE, warning=FALSE)

# Set the seed value.
seed = 0

# Set a custom color palette for plotting.
color_palette = c("#999999", "#E69F00", "#56B4E9", "#009E73",
                  "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# Set up the path to the participant data.
human_path = "data/human"

# Set up the path to the model data.
model_path = "data/model"
```

```{r libraries, echo=FALSE}
# Import R libraries.
library(boot)
library(tidyverse)
```

# Preprocessing

## Re-Label Participant Data

```{r preprocessing_relabel_participant_data}
# Read in the participant data.
human_0 = read_csv(file.path(human_path, "raw_data.csv"))

# Extract the participant data from the mentalistic condition.
human_1 = human_0 %>%
  filter(target_1!=-1) %>%
  select(workerid, layout, target_0, target_1) %>%
  rename(reward_0=target_0, cooperation=target_1)

# Extract the participant data from the non-mentalistic condition.
human_2 = human_0 %>%
  filter(target_1==-1) %>%
  select(workerid, layout, target_0) %>%
  rename(reward_1=target_0) %>%
  mutate(workerid=workerid-length(unique(workerid)))

# Merge the two data partitions and extract the layout information.
human_3 = human_1 %>%
  left_join(human_2)

# Extract the layout information and re-label the natural costs.
human_4 = human_3 %>%
  mutate(layout=substr(layout, 2, 12)) %>%
  separate(layout, into=c("natural_cost", "enforcer_action"), sep="_") %>%
  mutate(natural_cost=factor(natural_cost, 
                             levels=c("[5 5]", "[5 7]", "[5 9]",
                                      "[7 5]", "[7 7]", "[7 9]",
                                      "[9 5]", "[9 7]", "[9 9]"),
                             labels=c("[1.25 1.25]", "[1.25 1.75]",
                                      "[1.25 2.25]", "[1.75 1.25]",
                                      "[1.75 1.75]", "[1.75 2.25]",
                                      "[2.25 1.25]", "[2.25 1.75]",
                                      "[2.25 2.25]")))

# Write the preprocessed participant data.
write_csv(human_4, file.path(human_path, "data.csv"))

# Read in the participant age information.
age = read_csv(file.path(human_path, "subject_information.csv")) %>%
  select(workerid, age) %>%
  mutate(age=as.numeric(substr(age, 2, 3)))
```

## Compute Mean Participant Judgments

```{r preprocessing_compute_mean_participant_judgments}
# Read in the preprocessed participant data.
human_4 = read_csv(file.path(human_path, "data.csv"))

# Define the bootstrap functions
compute_mean = function(data, indices) {
  return(mean(data[indices]))
}

compute_bootstrap = function(data) {
  simulations = boot(data=data,
                     statistic=compute_mean,
                     R=10000)
  
  return(boot.ci(simulations, type="bca")$bca)
}

# Compute the bootstrapped 95% CIs for each dependent measure.
set.seed(seed)
ci = data.frame()
for (nc in unique(human_4$natural_cost)) {
  for (ea in unique(human_4$enforcer_action)) {
    # Filter the relevant data using the current natural cost and enforcer
    # action.
    human_5 = human_4 %>%
      filter(natural_cost==nc, enforcer_action==ea)
    
    # Compute the bootstrapped 95% CI for each dependent measure.
    reward_0_bootstrap = compute_bootstrap(human_5$reward_0)
    cooperation_bootstrap = compute_bootstrap(human_5$cooperation)
    reward_1_bootstrap = compute_bootstrap(human_5$reward_1)
    ci = rbind(ci, data.frame(natural_cost=nc,
                              enforcer_action=ea,
                              lower_ci_reward_0=reward_0_bootstrap[4],
                              upper_ci_reward_0=reward_0_bootstrap[5],
                              lower_ci_cooperation=cooperation_bootstrap[4],
                              upper_ci_cooperation=cooperation_bootstrap[5],
                              lower_ci_reward_1=reward_1_bootstrap[4],
                              upper_ci_reward_1=reward_1_bootstrap[5]))
  }
}

# Read in the model data.
model_0 = read_csv(file.path(model_path, "predictions.csv"))

# Compute the mean participant judgments for each dependent measure and merge
# the model data.
data_0 = human_4 %>%
  group_by(natural_cost, enforcer_action) %>%
  summarize(human_reward_0=mean(reward_0), human_cooperation=mean(cooperation),
            human_reward_1=mean(reward_1)) %>%
  left_join(ci) %>%
  left_join(select(model_0, -rationality, -enforcer_reward))
```

## Apply Min-Max Scaling

```{r preprocessing_apply_minmax_scaling}
# Extract the reward inferences from the mentalistic condition.
mentalistic_rewards = data_0 %>%
  select(natural_cost, enforcer_action, model_reward_0, human_reward_0,
         lower_ci_reward_0, upper_ci_reward_0) %>%
  rename(model=model_reward_0, participants=human_reward_0,
         lower=lower_ci_reward_0, upper=upper_ci_reward_0) %>%
  mutate(type="mentalistic_desires")

# Extract the reward inferences from the non-mentalistic condition.
nonmentalistic_rewards = data_0 %>%
  select(natural_cost, enforcer_action, model_reward_1, human_reward_1,
         lower_ci_reward_1, upper_ci_reward_1) %>%
  rename(model=model_reward_1, participants=human_reward_1,
         lower=lower_ci_reward_1, upper=upper_ci_reward_1) %>%
  mutate(type="non-mentalistic_desires")

# Merge the reward inferences from both conditions.
reward_inferences = mentalistic_rewards %>%
  rbind(nonmentalistic_rewards)

# Apply the min-max scaling to the reward inferences.
model_min = min(reward_inferences$model)
model_max = max(reward_inferences$model) - model_min
human_min = min(reward_inferences$participants)
human_max <- max(reward_inferences$participants) - human_min
data_1 = reward_inferences %>%
  mutate(model=(model-model_min)/model_max,
         participants=(participants-human_min)/human_max,
         lower=(lower-human_min)/human_max,
         upper=(upper-human_min)/human_max)

# Extract the cooperation inferences from the mentalistic condition.
cooperation_inferences = data_0 %>%
  select(natural_cost, enforcer_action, model_cooperation, human_cooperation,
         lower_ci_cooperation, upper_ci_cooperation) %>%
  rename(model=model_cooperation, participants=human_cooperation,
         lower=lower_ci_cooperation, upper=upper_ci_cooperation) %>%
  mutate(type="cooperation")

# Apply the min-max scaling to the cooperation inferences.
model_min = min(cooperation_inferences$model)
model_max = max(cooperation_inferences$model) - model_min
human_min = min(cooperation_inferences$participants)
human_max <- max(cooperation_inferences$participants) - human_min
data_2 = cooperation_inferences %>%
  mutate(model=(model-model_min)/model_max,
         participants=(participants-human_min)/human_max,
         lower=(lower-human_min)/human_max,
         upper=(upper-human_min)/human_max)

# Merge the min-max-scaled data.
data_3 = data_1 %>%
  rbind(data_2)
```

# Analysis of Main Results

Here we plot mean participant judgments ($N$=`r nrow(age)`, $M$=`r round(mean(age$age, na.rm=TRUE), 2)` years, $SD$=`r round(sd(age$age, na.rm=TRUE), 2)` years) against our model's predictions in both conditions jointly.

```{r main_results_plot, fig.align="center"}
# Plot the model predictions and mean participant judgments in both conditions.
plot_0 = data_3 %>%
  ggplot(aes(model, participants)) +
  geom_point(aes(fill=type), alpha=0.75, pch=21, size=4) +
  geom_smooth(method="lm", se=FALSE, color="black", linetype="dashed",
              size=0.5) +
  theme_classic() + 
  theme(aspect.ratio=1.0) +
  xlab("Model Predictions") + 
  ylab("Participant Judgments") +
  scale_fill_manual(name="Inference:",
                    limits=c("mentalistic_desires", "cooperation",
                             "non-mentalistic_desires"),
                    labels=c("Reward (M)", "Cooperation", "Reward (NM)"),
                    values=c(color_palette[3], color_palette[7],
                             color_palette[2]))
plot_0
```

```{r main_results_correlation}
# Define the bootstrap functions.
compute_cor = function(data, indices) {
  return(cor(data$model[indices], data$participants[indices],
             method="pearson"))
}

compute_bootstrap = function(data) {
  simulations = boot(data=data,
                     statistic=compute_cor,
                     R=10000)
  
  return(boot.ci(simulations, type="bca")$bca)
}

# Compute the correlation.
cor_0 = cor(data_3$model, data_3$participants)

# Compute the bootstrapped 95% CI of the correlation.
set.seed(seed)
cor_0_bootstrap = compute_bootstrap(data_3)
cor_0_ci = data.frame(
  lower=cor_0_bootstrap[4],
  upper=cor_0_bootstrap[5]
)
```

Our model predictions yield a correlation of $r$=`r round(cor_0, 2)` (95% CI: `r round(cor_0_ci$lower, 2)`-`r round(cor_0_ci$upper, 2)`) with participant judgments.

# Closer Look at Example Trials

Here we plot the data from a subset of our trials in greater detail.

## _Mentalistic_ Condition Examples

We first begin by plotting the data from the _mentalistic_ condition.

```{r mentalistic_condition_examples, fig.align="center"}
# Extract the data for a given natural cost and clamp the bootstrapped 95% CIs.
data_4 = data_3 %>%
  filter(natural_cost=="[2.25 2.25]") %>%
  gather(source, value, model, participants) %>%
  mutate(lower=ifelse(source=="model", NA, lower),
         lower=ifelse(lower<0, 0, lower),
         upper=ifelse(source=="model", NA, upper),
         upper=ifelse(upper>1, 1, upper))

# Plot the data from the example trials in the mentalistic condition.
plot_1 = data_4 %>%
  filter(type %in% c("mentalistic_desires", "cooperation")) %>%
  ggplot(aes(x=type, y=value, fill=source)) +
  geom_bar(stat="identity", position=position_dodge(), color="black") +
  geom_errorbar(aes(ymin=lower, ymax=upper), position=position_dodge(0.9),
                width=0.3) +
  facet_wrap(~factor(enforcer_action,
                     levels=c("[1 0]", "[2 0]", "[3 0]"),
                     labels=c("1 Boulder", "2 Boulders", "3 Boulders"))) +
  theme_classic() +
  theme(aspect.ratio=1.0) +
  scale_x_discrete(name="Inference",
                   limits=c("mentalistic_desires", "cooperation"),
                   labels=c("Reward (M)", "Cooperation")) +
  scale_y_continuous(name="Inferred Value",
                     expand=c(0, 0),
                     limits=c(0, 1.05)) +
  scale_fill_manual(name="Source:",
                    limits=c("model", "participants"),
                    labels=c("Model", "Participants"),
                    values=c(color_palette[8], color_palette[3]))
plot_1
```

## _Non-Mentalistic_ Condition Examples

Now we plot the data from the _non-mentalistic_ condition.

```{r non-mentalistic_condition_examples}
# Plot the data from the example trials in the non-mentalistic condition.
plot_2 = data_4 %>%
  filter(type %in% c("non-mentalistic_desires")) %>%
  ggplot(aes(x=type, y=value, fill=source)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.5,
           color="black") +
  geom_errorbar(aes(ymin=lower, ymax=upper), position=position_dodge(0.5),
                width=0.15) +
  facet_wrap(~factor(enforcer_action,
                     levels=c("[1 0]", "[2 0]", "[3 0]"),
                     labels=c("1 Boulder", "2 Boulders", "3 Boulders"))) +
  theme_classic() +
  theme(aspect.ratio=1.0) +
  scale_x_discrete(name="Inference",
                   limits=c("non-mentalistic_desires"),
                   labels=c("Reward (NM)")) +
  scale_y_continuous(name="Inferred Value",
                     expand=c(0, 0),
                     limits=c(0, 1.05)) +
  scale_fill_manual(name="Source:",
                    limits=c("model", "participants"),
                    labels=c("Model", "Participants"),
                    values=c(color_palette[8], color_palette[3]))
plot_2
```

# Decider Cost Lesion

Here we evaluate mean participant judgments ($N$=`r nrow(age)`, $M$=`r round(mean(age$age, na.rm=TRUE), 2)` years, $SD$=`r round(sd(age$age, na.rm=TRUE), 2)` years) against our model's performance when deciders no longer have an understanding of costs--that is, they navigate the world with their rewards as their only consideration.

## Preprocessing

### Apply Min-Max Scaling

```{r decider_cost_lesion_preprocessing}
# Read in the model predictions of the "decider cost lesion" model.
model_1 = read_csv(file.path(model_path,
                             "decider_cost_lesion/predictions.csv"))

# Compute the mean participant judgments for each dependent measure and merge
# the model data.
data_5 = human_4 %>%
  group_by(natural_cost, enforcer_action) %>%
  summarize(human_reward_0=mean(reward_0), human_cooperation=mean(cooperation),
            human_reward_1=mean(reward_1)) %>%
  left_join(ci) %>%
  left_join(select(model_1, -rationality, -enforcer_reward))

# Extract the reward inferences from the mentalistic condition.
mentalistic_rewards = data_5 %>%
  select(natural_cost, enforcer_action, model_reward_0, human_reward_0,
         lower_ci_reward_0, upper_ci_reward_0) %>%
  rename(model=model_reward_0, participants=human_reward_0,
         lower=lower_ci_reward_0, upper=upper_ci_reward_0) %>%
  mutate(type="mentalistic_desires")

# Extract the reward inferences from the non-mentalistic condition.
nonmentalistic_rewards = data_5 %>%
  select(natural_cost, enforcer_action, model_reward_1, human_reward_1,
         lower_ci_reward_1, upper_ci_reward_1) %>%
  rename(model=model_reward_1, participants=human_reward_1,
         lower=lower_ci_reward_1, upper=upper_ci_reward_1) %>%
  mutate(type="non-mentalistic_desires")

# Merge the reward inferences from both conditions.
reward_inferences = mentalistic_rewards %>%
  rbind(nonmentalistic_rewards)

# Apply the min-max scaling to the reward inferences.
model_min = min(reward_inferences$model)
model_max = max(reward_inferences$model) - model_min
human_min = min(reward_inferences$participants)
human_max <- max(reward_inferences$participants) - human_min
data_6 = reward_inferences %>%
  mutate(model=(model-model_min)/model_max,
         participants=(participants-human_min)/human_max,
         lower=(lower-human_min)/human_max,
         upper=(upper-human_min)/human_max)

# Extract the cooperation inferences from the mentalistic condition.
cooperation_inferences = data_5 %>%
  select(natural_cost, enforcer_action, model_cooperation, human_cooperation,
         lower_ci_cooperation, upper_ci_cooperation) %>%
  rename(model=model_cooperation, participants=human_cooperation,
         lower=lower_ci_cooperation, upper=upper_ci_cooperation) %>%
  mutate(type="cooperation")

# Apply the min-max scaling to the cooperation inferences.
model_min = min(cooperation_inferences$model)
model_max = max(cooperation_inferences$model) - model_min
human_min = min(cooperation_inferences$participants)
human_max <- max(cooperation_inferences$participants) - human_min
data_7 = cooperation_inferences %>%
  mutate(model=(model-model_min)/model_max,
         participants=(participants-human_min)/human_max,
         lower=(lower-human_min)/human_max,
         upper=(upper-human_min)/human_max)

# Merge the min-max-scaled data.
data_8 = data_6 %>%
  rbind(data_7)
```

## Analysis of "Decider Cost Lesion" Model Results

```{r decider_cost_lesion_results_plot, fig.align="center"}
# Plot the model predictions and mean participant judgments in both conditions
# for the "decider cost lesion" model.
plot_3 = data_8 %>%
  ggplot(aes(model, participants)) +
  geom_point(aes(fill=type), alpha=0.75, pch=21, size=4) +
  geom_smooth(method="lm", se=FALSE, color="black", linetype="dashed",
              size=0.5) +
  theme_classic() + 
  theme(aspect.ratio=1.0) +
  xlab("Model Predictions") + 
  ylab("Participant Judgments") +
  scale_fill_manual(name="Inference:",
                    limits=c("mentalistic_desires", "cooperation",
                             "non-mentalistic_desires"),
                    labels=c("Reward (M)", "Cooperation", "Reward (NM)"),
                    values=c(color_palette[3], color_palette[7],
                             color_palette[2]))
plot_3
```

```{r decider_cost_lesion_results_correlation}
# Define the bootstrap functions.
compute_cor = function(data, indices) {
  return(cor(data$model[indices], data$participants[indices],
             method="pearson"))
}

compute_bootstrap = function(data) {
  simulations = boot(data=data,
                     statistic=compute_cor,
                     R=10000)
  
  return(boot.ci(simulations, type="bca")$bca)
}

# Compute the correlation.
cor_1 = cor(data_8$model, data_8$participants)

# Compute the bootstrapped 95% CI for the correlation.
set.seed(seed)
cor_1_bootstrap = compute_bootstrap(data_8)
cor_1_ci = data.frame(
  lower=cor_1_bootstrap[4],
  upper=cor_1_bootstrap[5]
)
```

Our "decider cost lesion" model predictions yield a correlation of $r$=`r round(cor_1, 2)` (95% CI: `r round(cor_1_ci$lower, 2)`-`r round(cor_1_ci$upper, 2)`) with participant judgments.

# Enforcer Cost Lesion

Now we evaluate mean participant judgments ($N$=`r nrow(age)`, $M$=`r round(mean(age$age, na.rm=TRUE), 2)` years, $SD$=`r round(sd(age$age, na.rm=TRUE), 2)` years) against our model's performance when enforcers no longer have an understanding of costs--that is, they manipulate the environment with their rewards as their only consideration.

## Preprocessing

### Apply Min-Max Scaling

```{r enforcer_cost_lesion_preprocessing}
# Read in the model predictions of the "enforcer cost lesion" model.
model_2 = read_csv(file.path(model_path,
                             "enforcer_cost_lesion/predictions.csv"))
# Compute the mean participant judgments for each dependent measure and merge
# the model data.
data_9 = human_4 %>%
  group_by(natural_cost, enforcer_action) %>%
  summarize(human_reward_0=mean(reward_0), human_cooperation=mean(cooperation),
            human_reward_1=mean(reward_1)) %>%
  left_join(ci) %>%
  left_join(select(model_2, -rationality, -enforcer_reward))

# Extract the reward inferences from the mentalistic condition.
mentalistic_rewards = data_9 %>%
  select(natural_cost, enforcer_action, model_reward_0, human_reward_0,
         lower_ci_reward_0, upper_ci_reward_0) %>%
  rename(model=model_reward_0, participants=human_reward_0,
         lower=lower_ci_reward_0, upper=upper_ci_reward_0) %>%
  mutate(type="mentalistic_desires")

# Extract the reward inferences from the non-mentalistic condition.
nonmentalistic_rewards = data_9 %>%
  select(natural_cost, enforcer_action, model_reward_1, human_reward_1,
         lower_ci_reward_1, upper_ci_reward_1) %>%
  rename(model=model_reward_1, participants=human_reward_1,
         lower=lower_ci_reward_1, upper=upper_ci_reward_1) %>%
  mutate(type="non-mentalistic_desires")

# Merge the reward inferences from both conditions.
reward_inferences = mentalistic_rewards %>%
  rbind(nonmentalistic_rewards)

# Apply the min-max scaling to the reward inferences.
model_min = min(reward_inferences$model)
model_max = max(reward_inferences$model) - model_min
human_min = min(reward_inferences$participants)
human_max <- max(reward_inferences$participants) - human_min
data_10 = reward_inferences %>%
  mutate(model=(model-model_min)/model_max,
         participants=(participants-human_min)/human_max,
         lower=(lower-human_min)/human_max,
         upper=(upper-human_min)/human_max)

# Extract the cooperation inferences from the mentalistic condition.
cooperation_inferences = data_9 %>%
  select(natural_cost, enforcer_action, model_cooperation, human_cooperation,
         lower_ci_cooperation, upper_ci_cooperation) %>%
  rename(model=model_cooperation, participants=human_cooperation,
         lower=lower_ci_cooperation, upper=upper_ci_cooperation) %>%
  mutate(type="cooperation")

# Apply the min-max scaling to the cooperation inferences.
model_min = min(cooperation_inferences$model)
model_max = max(cooperation_inferences$model) - model_min
human_min = min(cooperation_inferences$participants)
human_max <- max(cooperation_inferences$participants) - human_min
data_11 = cooperation_inferences %>%
  mutate(model=(model-model_min)/model_max,
         participants=(participants-human_min)/human_max,
         lower=(lower-human_min)/human_max,
         upper=(upper-human_min)/human_max)

# Merge the min-max-scaled data.
data_12 = data_10 %>%
  rbind(data_11)
```

## Analysis of Enforcer Cost Lesion Results

```{r enforcer_cost_lesion_results_plot, fig.align="center"}
# Plot the model predictions and mean participant judgments in both conditions
# for the "enforcer cost lesion" model.
plot_4 = data_12 %>%
  ggplot(aes(model, participants)) +
  geom_point(aes(fill=type), alpha=0.75, pch=21, size=4) +
  geom_smooth(method="lm", se=FALSE, color="black", linetype="dashed",
              size=0.5) +
  theme_classic() + 
  theme(aspect.ratio=1.0) +
  xlab("Model Predictions") + 
  ylab("Participant Judgments") +
  scale_fill_manual(name="Inference:",
                    limits=c("mentalistic_desires", "cooperation",
                             "non-mentalistic_desires"),
                    labels=c("Reward (M)", "Cooperation", "Reward (NM)"),
                    values=c(color_palette[3], color_palette[7],
                             color_palette[2]))
plot_4
```

```{r enforcer_cost_lesion_results_correlation}
# Define the bootstrap functions.
compute_cor = function(data, indices) {
  return(cor(data$model[indices], data$participants[indices],
             method="pearson"))
}

compute_bootstrap = function(data) {
  simulations = boot(data=data,
                     statistic=compute_cor,
                     R=10000)
  
  return(boot.ci(simulations, type="bca")$bca)
}

# Compute the correlation.
cor_2 = cor(data_12$model, data_12$participants)

# Compute the bootstrapped 95% CI for the correlation.
set.seed(seed)
cor_2_bootstrap = compute_bootstrap(data_12)
cor_2_ci = data.frame(
  lower=cor_2_bootstrap[4],
  upper=cor_2_bootstrap[5]
)
```

Our "enforcer cost lesion" model predictions yield a correlation of $r$=`r round(cor_2, 2)` (95% CI: `r round(cor_2_ci$lower, 2)`-`r round(cor_2_ci$upper, 2)`) with participant judgments.

# Full Model vs. Lesioned Models

```{r full_model_vs_lesioned_models}
# Define the boostrap functions.
compute_cor_diff = function(data, indices) {
  cor_full_model = cor(data$full_model[indices],
                       data$participants[indices],
                       method="pearson")
  cor_lesioned_model = cor(data$lesioned_model[indices],
                           data$participants[indices],
                           method="pearson")
  return(cor_full_model-cor_lesioned_model)
}

# Define the bootstrap function to simulate the data.
compute_bootstrap = function(data) {
  simulations = boot(data=data,
                     statistic=compute_cor_diff,
                     R=10000)
  
  return(boot.ci(simulations, type="bca")$bca)
}

# Merge the full model data with the data from the "decider cost lesion" model.
data_13 = data_3 %>%
  rename(full_model=model) %>%
  left_join(rename(data_8, lesioned_model=model))

# Compute the correlation difference between the full model and the "decider
# cost lesion" model.
cor_diff_0 = cor_0 - cor_1

# Compute the bootstrapped 95% CI for the correlation difference.
set.seed(seed)
cor_diff_0_bootstrap = compute_bootstrap(data_13)
cor_diff_0_ci = data.frame(
  lower=cor_diff_0_bootstrap[4],
  upper=cor_diff_0_bootstrap[5]
)

# Merge the full model data with the data from the "enforcer cost lesion" model.
data_14 = data_3 %>%
  rename(full_model=model) %>%
  left_join(rename(data_12, lesioned_model=model))

# Compute the correlation difference between the full model and the "enforcer
# cost lesion" model.
cor_diff_1 = cor_0 - cor_2

# Compute the bootstrapped 95% CI for the correlation difference.
set.seed(seed)
cor_diff_1_bootstrap = compute_bootstrap(data_14)
cor_diff_1_ci = data.frame(
  lower=cor_diff_1_bootstrap[4],
  upper=cor_diff_1_bootstrap[5]
)
```

When compared against the "decider cost lesion" model, our model has a correlation difference of $\Delta r$=`r round(cor_diff_0, 2)` (95% CI: `r round(cor_diff_0_ci$lower, 2)`-`r round(cor_diff_0_ci$upper, 2)`). When compared against the "enforcer cost lesion" model, our model as a correlation difference of $\Delta r$=`r round(cor_diff_1, 2)` (95% CI: `r round(cor_diff_1_ci$lower, 2)`-`r round(cor_diff_1_ci$upper, 2)`).
