---
title: "Physical Pragmatics (decider_3)"
output:
  pdf_document: default
  html_document:
    code_folding: hide
    df_print: paged
---
  
```{r setup, echo=FALSE}
# Set the working directory.
knitr::opts_knit$set(root.dir=normalizePath("../.."))

# Turn off compile messages and warnings.
knitr::opts_chunk$set(message=FALSE, warning=FALSE)

# Set the seed value.
seed = 0

# Set up the path to each partition of the participant data.
data_path = "data/decider_3/data_0"
```

```{r libraries, echo=FALSE}
# Import R libraries.
library(boot)
library(jsonlite)
library(tidyverse)
```

# Preprocessing

```{r preprocessing}
# Read in the participant data.
data_0 = read_csv(file.path(data_path, "raw_data.csv"), quote="~")

# Convert the JSON string into JSON.
data_1 = lapply(data_0$data, fromJSON)

# Extract the trial information for each participant and stack them.
data_3 = tibble()
for (p in 1:length(data_1)) {
  # Trim the map and add the participant ID back in.
  data_2 = data_1[p][[1]]$trials %>%
    as.data.frame() %>%
    gather(type, num, trial_num, exclusion_num) %>%
    na.omit() %>%
    mutate(type=gsub("num", "", type)) %>%
    mutate(target=as.numeric(target), trial=paste(type, num, sep=""),
           object=data_1[p][[1]]$setup$object,
           condition=data_1[p][[1]]$setup$condition,
           unique_id=data_1[p][[1]]$id,
           age=as.numeric(data_1[p][[1]]$subject_information$age)) %>%
    select(-type, -num)
  
  # Stack the trial information for the current participant.
  data_3 = rbind(data_3, data_2)
}

# Exclude participants that said the unmodified door was harder to walk
# through.
data_5 = tibble()
exclusions = tibble()
for (participant in unique(data_3$unique_id)) {
  data_4 = data_3 %>%
    filter(unique_id==participant)

  if (filter(data_4, trial=="exclusion_1")[,"target"]==0) {
    exclusions = rbind(exclusions, data_4)
  }
  else {
    data_5 = rbind(data_5, data_4)
  }
}

# Write the preprocessed data.
write_csv(data_5, file.path(data_path, "data.csv"))
```

# Compute Door Endorsement

## _a priori_ Labels

First, we'll compute the participant endorsement ($N$=`r length(filter(data_5, trial=="trial_1")$unique_id)`, $M$=`r round(mean(filter(data_5, trial=="trial_1")$age, na.rm=TRUE), 2)` years, $SD$=`r round(sd(filter(data_5, trial=="trial_1")$age, na.rm=TRUE), 2)` years) for the unmodified door (i.e., that the modified door should be avoided) using our _a priori_ labels of door difficulty.

```{r compute_endorsement_a_priori_labels, fig.align="center"}
# Read in the preprocessed data.
data_6 = read_csv(file.path(data_path, "data.csv"))

# Filter the trial of interest.
data_7 = data_6 %>%
  filter(trial=="trial_1")

# Set up the bootstrap functions.
compute_mean = function(data, indices) {
  return(mean(data[indices]))
}

compute_bootstrap = function(data) {
  simulations = boot(data=data$target,
                     statistic=compute_mean,
                     R=10000)
  
  return(boot.ci(simulations, type="perc")$perc)
}

# Set the seed and compute the 95% bootstrapped CIs.
set.seed(seed)
ci = data.frame()
bootstrap_data = compute_bootstrap(filter(data_7, condition=="none"))
ci = rbind(ci, data.frame(lower_ci=bootstrap_data[4]*100,
                          upper_ci=bootstrap_data[5]*100,
                          condition="none"))

bootstrap_data = compute_bootstrap(filter(data_7, condition=="low"))
ci = rbind(ci, data.frame(lower_ci=ifelse(!is.null(bootstrap_data),
                                          bootstrap_data[4]*100, 100),
                          upper_ci=ifelse(!is.null(bootstrap_data),
                                          bootstrap_data[5]*100, 100),
                          condition="low"))

# Convert individual judgments to aggregate percentages.
data_8 = data_7 %>%
  group_by(condition) %>%
  summarize(unmodified=sum(target)/n()*100, modified=100-unmodified) %>%
  gather(response, endorsement, unmodified, modified) %>%
  left_join(ci)

# Plot the data (using our labels of door difficulty).
plot_0 = data_8 %>%
  ggplot(aes(x=condition, y=endorsement, fill=response)) + 
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=lower_ci, ymax=upper_ci), width=0.2) +
  geom_hline(yintercept=50, linetype="dashed", color="black") +
  theme_classic() +
  theme(aspect.ratio=1.0,
        legend.title=element_text(hjust=0.5)) +
  ylab("Endorsement (%)") +
  scale_x_discrete(name="Condition",
                   limits=c("none", "low"),
                   labels=c("No-Cost", "Low-Cost")) +
  scale_fill_discrete(name="Response",
                      limits=c("modified", "unmodified"),
                      labels=c("Modified", "Unmodified"))
plot_0
```

```{r compute_statistics_a_priori_labels}
# Compute a t-test with the alternative hypothesis that the participant 
# endorsement of the unmodified door is above chance.
data_9 = filter(data_7, condition=="none")
t.test(x=data_9$target, n=length(data_9$target), mu=0.5, alternative="greater")

# Compute a t-test with the alternative hypothesis that the participant
# endorsement of the unmodified door in the low-cost condition is higher than
# in the no-cost condition.
data_10 = filter(data_7, condition=="low")
t.test(x=data_10$target, y=data_9$target, alternative="greater")
```

## Participant Labels

Now, we'll analyze the participant endorsement ($N$=`r length(filter(data_5, trial=="trial_1")$unique_id)`, $M$=`r round(mean(filter(data_5, trial=="trial_1")$age, na.rm=TRUE), 2)` years, $SD$=`r round(sd(filter(data_5, trial=="trial_1")$age, na.rm=TRUE), 2)` years) for the unmodified door (i.e., that the modified door should be avoided) using participant labels of door difficulty.

```{r compute_endorsement_participant_labels, fig.align="center"}
# Filter the trial of interest.
data_11 = data_6 %>%
  spread(trial, target) %>%
  mutate(condition=ifelse(exclusion_1==1, "low", "none")) %>%
  select(-exclusion_1, -exclusion_2) %>%
  rename(target=trial_1)

# Set the seed and compute the 95% bootstrapped CIs.
set.seed(seed)
ci = data.frame()
bootstrap_data = compute_bootstrap(filter(data_11, condition=="none"))
ci = rbind(ci, data.frame(lower_ci=bootstrap_data[4]*100,
                          upper_ci=bootstrap_data[5]*100,
                          condition="none"))

bootstrap_data = compute_bootstrap(filter(data_11, condition=="low"))
ci = rbind(ci, data.frame(lower_ci=ifelse(!is.null(bootstrap_data),
                                          bootstrap_data[4]*100, 100),
                          upper_ci=ifelse(!is.null(bootstrap_data),
                                          bootstrap_data[5]*100, 100),
                          condition="low"))

# Convert individual judgments to aggregate percentages.
data_12 = data_11 %>%
  group_by(condition) %>%
  summarize(unmodified=sum(target)/n()*100, modified=100-unmodified) %>%
  gather(response, endorsement, unmodified, modified) %>%
  left_join(ci)

# Plot the data (using participant labels of door difficulty).
plot_1 = data_12 %>%
  ggplot(aes(x=condition, y=endorsement, fill=response)) + 
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=lower_ci, ymax=upper_ci), width=0.2) +
  geom_hline(yintercept=50, linetype="dashed", color="black") +
  theme_classic() +
  theme(aspect.ratio=1.0,
        legend.title=element_text(hjust=0.5)) +
  ylab("Endorsement (%)") +
  scale_x_discrete(name="Participant-Judged Condition",
                   limits=c("none", "low"),
                   labels=c("No-Cost", "Low-Cost")) +
  scale_fill_discrete(name="Response",
                      limits=c("modified", "unmodified"),
                      labels=c("Modified", "Unmodified"))
plot_1
```

```{r compute_statistics_participant_labels}
# Compute a t-test with the alternative hypothesis that the participant 
# endorsement of the unmodified door is above chance.
data_13 = filter(data_11, condition=="none")
t.test(x=data_13$target, n=length(data_13$target), mu=0.5,
       alternative="greater")

# Compute a t-test with the alternative hypothesis that the participant
# endorsement of the unmodified door in the low-cost condition is higher than
# in the no-cost condition.
data_14 = filter(data_11, condition=="low")
t.test(x=data_14$target, y=data_13$target, alternative="greater")
```
